
 \begin{thebibliography}{9}

	\bibitem{lamport94}
	S. Melnik, H. Garcia-Molina and E. Rahm, 
	\emph{Similarity flooding: a versatile graph matching algorithm and its application to schema matching},
	in Proceedings 18th ICDE, San Jose
	CA, Feb 2002.
	
	\bibitem{lamport94}
	L. Cordella, P. Foggia, C. Sansone, and M. Vento, 
	\emph{“A (sub)graph isomorphism algorithm for matching large graphs”},
	IEEE Transactions on Pattern Analysis and Machine Intelligence,
	vol. 26, no. 10, pp. 1367–1372, Oct. 2004.
	
	\bibitem{lamport94}
	Marshall, B., Chen, H., Madhusudan, T. (2006),
	\emph{Matching knowledge elements in concept maps using a similarity flooding algorithm. Decision Support Systems},
	42 (3), 1290-1306.	
	
	\bibitem{lamport94}
	\emph{VF2 Algorithm(2015)},
	Available at: \url{https://networkx.github.io/documentation/latest/reference/algorithms.isomorphism.vf2.html},
	(Accessed: 10 April 2015).
	
	\bibitem{lamport94}
	P. Foggia, C. Sansone, M. Vento,
	\emph{“A performance comparison of five algorithms for graph isomorphism“},
	submitted for publication to the Third TC-15 International Workshop on Graph Based Representation, Italy, 2001.
	
	\bibitem{lamport94}
	L.P. Cordella, P. Foggia, C. Sansone, M. Vento, 
	\emph{Evaluating Performance of the VF Graph Matching Algorithm, Proc. of the 10th International Conference on Image	Analysis and Processing},
	IEEE Computer Society Press, pp. 1172-1177, 1999.

	\bibitem{lamport94}
	N.J. Nilsson, 
	\emph{Principles of Artificial Intelligence},
	Springer-Verlag, 1982.	
	
	\bibitem{lamport94}
	J.R. Ullmann, 
	\emph{An Algorithm for Subgraph Isomorphism, Journal of the Association for Computing Machinery},
	vol. 23, pp. 31-42, 1976.
	
	\bibitem{lamport94}
	B. T. Messmer, 
	\emph{Efficient Graph Matching Algorithms for Preprocessed Model	Graphs},
	Ph.D. Thesis, Inst. of Comp. Sci. and Applied Mathematics,
	University of Bern, 1996.
	
	\bibitem{lamport94}
	H. Ehrig, 
	\emph{“Introduction to Graph Grammars with Applications to Semantic Networks”},
	Comput. Math. Appl. 23, pp. 557-572, 1992.
	
	\bibitem{lamport94}
	D.H. Rouvray, A.T. Balaban,
	\emph{“Chemichal Applications of Graph Theory” in Applications of Graph Theory},
	Academic Press, New York, pp.177-221, 1979.
	
	\bibitem{lamport94}
	Reinhard Diestel, 
	\emph{Graph Theory},
	Graduate Texts in Mathematics,
	Vol. 173, Springer Verlag, Berlin, 1991.

\end{thebibliography}